Model complexity and model choice for animal movement models

### 2016-06-09 guelph_talk/guelph_panther.Rnw
almost final version?

<<cat1sumdat,echo=FALSE,cache=TRUE>>=
L <- load("../cat1sumdat.RData")
ss <- sumdat %>% filter(grepl("HMM",type)) %>%
    mutate(deltaBIC=deltaBIC-min(deltaBIC),
           model=factor(model,
              levels=c("HMM","HMM + THsin","HMM + THquad",
                       "HMM + THblock", "HMM + THhourly"),
              labels=c("homogeneous","sinusoid","quadratic",
                       "block","hourly")))
@

@@

@@

\begin{frame}
\frametitle{Animal movement: open challenges}
\begin{itemize}
\item Cognition/memory \citepx{bracis_memory_2015}
\item Intraspecific interaction/collective movement \citepx{delgado_statistical_2014}
\item Continuous-time movement models \citepx{calabrese_ctmm_2016}
\item Edges, barriers, and corridors \citepx{beyer_you_2016}
\item Efficient (big-data) approaches \citepx{brillinger_three_2008}
\item Putting it all together ...
\end{itemize}
\end{frame}

>>>>

<<cat1sumdat,echo=FALSE,cache=TRUE>>=
L <- load("../cat1sumdat.RData")
ss <- sumdat %>% filter(grepl("HMM",type)) %>%
    mutate(deltaBIC=deltaBIC-min(deltaBIC),
           model=factor(model,
              levels=c("HMM","HMM + THquad","HMM + THsin",
                       "HMM + THblock", "HMM + THhourly"),
              labels=c("homogeneous","quadratic","sinusoid",
                       "block","hourly")))
@

@@

\begin{frame}
\frametitle{Model complexity: simulation}
<<modsim>>=
mnames3 <- c("hmm","hmmquad",
            "hmmsin","hmmhourly")
mnames4 <- c("homogeneous",
             "quadratic","sin","hourly")
simdf2 <- readRDS("../simdf.RDS") %>%
    filter(!type %in% c("fmm","fmmsin")) %>%
    group_by(type) %>%
    mutate(dBIC=BIC-min(BIC)) %>% ungroup() %>%
    mutate(type=factor(type,levels=mnames3,labels=mnames4))
ggplot(simdf2,aes(states,dBIC,colour=type))+
    geom_point(size=2)+geom_line()+
    scale_colour_brewer(palette="Dark2")+
    labs(y=expression(paste(Delta, "BIC")),
         x="number of latent states")
@
\end{frame}

@@

\begin{frame}
\frametitle{Animal movement: open challenges}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}
\item Cognition/memory \citepx{bracis_memory_2015}
\item Intraspecific interaction/collective movement \citepx{delgado_statistical_2014}
\item Continuous-time movement models \citepx{calabrese_ctmm_2016}
\item Edges, barriers, and corridors \citepx{beyer_you_2016}
\item Efficient (big-data) approaches \citepx{brillinger_three_2008}
\item Putting it all together ...
\end{itemize}
\end{column}
\begin{column}{0.5\textwidth}
\includegraphics[width=\textwidth]{pix/kitchensink.jpg}
\end{column}
\end{columns}
\end{frame}
